GSE74548: Preparation

### 2023-09-15 figs/step_01a_GSE74548_prep.Rmd
rownames for design matrix

design <- model.matrix(~ age+ sex + groups)
mxs <- mx[,which( colnames(mx) %in% rownames(samplesheet) )]
saveRDS(mxs,"dm3_mx.Rds")
saveRDS(design,"dm3_design.Rds")

>>>>

design <- model.matrix(~ age+ sex + groups)
mxs <- mx[,which( colnames(mx) %in% rownames(samplesheet) )]
saveRDS(mxs,"dm3_mx.Rds")
rownames(design) <- rownames(samplesheet)
head(design)
saveRDS(design,"dm3_design.Rds")
